---
title: "Voting patterns"
output: html_document
date: "2024-05-18"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, include=FALSE}
library(ggplot2)
library(tidyverse)
library(pastecs)
library(dplyr)
library(gridExtra)
library(stringi)
library(WRS2)
library(car)
library(readxl)
library(janitor)
library(fedmatch)#(https://cran.r-project.org/web/packages/fedmatch/vignettes/Fuzzy-matching.html)
library(broom)
library(knitr)
library(car)
library(dlookr)
library(flextable)
library(rstanarm)
library(performance)
```

# Load the data
```{r}
# Define the ranges for the file names
range_1 <- 1:20
range_2 <- c(16, 18)
range_3 <- c(80, 100)

# Base directory where the CSV files are stored
base_dir <- "Data/CSV/"

# Initialize an empty list to store the data frames
turtles_data <- list()

# Loop over the ranges and read the files dynamically
for (i in range_1) {
  for (j in range_2) {
    for (k in range_3) {
      # Construct the file name
      file_name <- sprintf("TURTLES_%d_%d_%d.csv", i, j, k)
      file_path <- file.path(base_dir, file_name)
      
      # Read the CSV file and store it in the list
      if (file.exists(file_path)) {
        data_name <- sprintf("Turtles%d_%d_%d", i, j, k)
        turtles_data[[data_name]] <- read.csv(file_path)
      } else {
        message(sprintf("File not found: %s", file_path))
      }
    }
  }
}

# You can now access the data frames from the turtles_data list
# For example, to access the data frame for Turtles1_16_80:
print(turtles_data$Turtles1_16_80)

# Optionally, you can assign the data frames to variables in the global environment
for (name in names(turtles_data)) {
  assign(name, turtles_data[[name]])
}
```

#Bind df together and add sim number for first 10 sims
```{r}
Turtles1_16_80$sim <- 1
Turtles2_16_80$sim <- 2
Turtles3_16_80$sim <- 3
Turtles4_16_80$sim <- 4
Turtles5_16_80$sim <- 5
Turtles6_16_80$sim <- 6
Turtles7_16_80$sim <- 7
Turtles8_16_80$sim <- 8
Turtles9_16_80$sim <- 9
Turtles10_16_80$sim <- 10
Turtles1_18_80$sim <- 1
Turtles2_18_80$sim <- 2
Turtles3_18_80$sim <- 3
Turtles4_18_80$sim <- 4
Turtles5_18_80$sim <- 5
Turtles6_18_80$sim <- 6
Turtles7_18_80$sim <- 7
Turtles8_18_80$sim <- 8
Turtles9_18_80$sim <- 9
Turtles10_18_80$sim <- 10
Turtles1_16_100$sim <- 1
Turtles2_16_100$sim <- 2
Turtles3_16_100$sim <- 3
Turtles4_16_100$sim <- 4
Turtles5_16_100$sim <- 5
Turtles6_16_100$sim <- 6
Turtles7_16_100$sim <- 7
Turtles8_16_100$sim <- 8
Turtles9_16_100$sim <- 9
Turtles10_16_100$sim <- 10
Turtles1_18_100$sim <- 1
Turtles2_18_100$sim <- 2
Turtles3_18_100$sim <- 3
Turtles4_18_100$sim <- 4
Turtles5_18_100$sim <- 5
Turtles6_18_100$sim <- 6
Turtles7_18_100$sim <- 7
Turtles8_18_100$sim <- 8
Turtles9_18_100$sim <- 9
Turtles10_18_100$sim <- 10

df_16_80_first10 <- rbind(Turtles1_16_80, Turtles2_16_80, Turtles3_16_80, Turtles4_16_80, Turtles5_16_80, Turtles6_16_80, Turtles7_16_80, Turtles8_16_80, Turtles9_16_80, Turtles10_16_80)
df_16_100_first10 <- rbind(Turtles1_16_100, Turtles2_16_100, Turtles3_16_100, Turtles4_16_100, Turtles5_16_100, Turtles6_16_100, Turtles7_16_100, Turtles8_16_100, Turtles9_16_100, Turtles10_16_100)
df_18_80_first10 <- rbind(Turtles1_18_80, Turtles2_18_80, Turtles3_18_80, Turtles4_18_80, Turtles5_18_80, Turtles6_18_80, Turtles7_18_80, Turtles8_18_80, Turtles9_18_80, Turtles10_18_80)
df_18_100_first10 <- rbind(Turtles1_18_100, Turtles2_18_100, Turtles3_18_100, Turtles4_18_100, Turtles5_18_100, Turtles6_18_100, Turtles7_18_100, Turtles8_18_100, Turtles9_18_100, Turtles10_18_100)
```

# Visualizations
```{r}
grid.arrange(
  ggplot(df_16_80_first10, aes(x = vote, fill = factor(sim))) +
  geom_histogram(binwidth = 1, color = "white", alpha = 0.7, position = "dodge") +
  labs(title = "Age 16-80", x = "Vote", y = "Frequency") +
  theme_minimal() +
  scale_fill_manual(values = c("red", "blue", "green4", "purple", "darkorange", "black", "lightblue", "hotpink", "yellow", "magenta" )) +
  guides(fill = guide_legend(title = "Simulation")),
  
  ggplot(df_16_100_first10, aes(x = vote, fill = factor(sim))) +
  geom_histogram(binwidth = 1, color = "white", alpha = 0.7, position = "dodge") +
  labs(title = "Age 16-100", x = "Vote", y = "Frequency") +
  theme_minimal() +
  scale_fill_manual(values = c("red", "blue", "green4", "purple", "darkorange", "black", "lightblue", "hotpink", "yellow", "magenta")) +
  guides(fill = guide_legend(title = "Simulation")),
  
  ggplot(df_18_80_first10, aes(x = vote, fill = factor(sim))) +
  geom_histogram(binwidth = 1, color = "white", alpha = 0.7, position = "dodge") +
  labs(title = "Age 18-80", x = "Vote", y = "Frequency") +
  theme_minimal() +
  scale_fill_manual(values = c("red", "blue", "green4", "purple", "darkorange", "black", "lightblue", "hotpink", "yellow", "magenta")) +
  guides(fill = guide_legend(title = "Simulation")),
  
  ggplot(df_18_100_first10, aes(x = vote, fill = factor(sim))) +
  geom_histogram(binwidth = 1, color = "white", alpha = 0.7, position = "dodge") +
  labs(title = "Age 18-100", x = "Vote", y = "Frequency") +
  theme_minimal() +
  scale_fill_manual(values = c("red", "blue", "green4", "purple", "darkorange", "black", "lightblue", "hotpink", "yellow", "magenta")) +
  guides(fill = guide_legend(title = "Simulation")),
  
  nrow = 2, ncol = 2
)
```

```{r}
grid.arrange(
ggplot(Turtles1_16_80, aes(x = vote)) +
  geom_histogram(binwidth = 1, fill = "blue", color = "black", alpha = 0.7) +
  labs(title = "Sim 1; 16-80", x = "Vote", y = "Frequency") +
  theme_minimal(),

ggplot(Turtles2_16_80, aes(x = vote)) +
  geom_histogram(binwidth = 1, fill = "red", color = "black", alpha = 0.7) +
  labs(title = "Sim 2; 16-80", x = "Vote", y = "Frequency") +
  theme_minimal(),

ggplot(Turtles3_16_80, aes(x = vote)) +
  geom_histogram(binwidth = 1, fill = "green4", color = "black", alpha = 0.7) +
  labs(title = "Sim 3; 16-80", x = "Vote", y = "Frequency") +
  theme_minimal(),

ggplot(Turtles4_16_80, aes(x = vote)) +
  geom_histogram(binwidth = 1, fill = "orange", color = "black", alpha = 0.7) +
  labs(title = "Sim 4; 16-80", x = "Vote", y = "Frequency") +
  theme_minimal(),

ggplot(Turtles5_16_80, aes(x = vote)) +
  geom_histogram(binwidth = 1, fill = "purple", color = "black", alpha = 0.7) +
  labs(title = "Sim 5; 16-80", x = "Vote", y = "Frequency") +
  theme_minimal(),

ggplot(Turtles1_16_100, aes(x = vote)) +
  geom_histogram(binwidth = 1, fill = "blue", color = "black", alpha = 0.7) +
  labs(title = "Sim 1; 16-100", x = "Vote", y = "Frequency") +
  theme_minimal(),

ggplot(Turtles2_16_100, aes(x = vote)) +
  geom_histogram(binwidth = 1, fill = "red", color = "black", alpha = 0.7) +
  labs(title = "Sim 2; 16-100", x = "Vote", y = "Frequency") +
  theme_minimal(),

ggplot(Turtles3_16_100, aes(x = vote)) +
  geom_histogram(binwidth = 1, fill = "green4", color = "black", alpha = 0.7) +
  labs(title = "Sim 3; 16-100", x = "Vote", y = "Frequency") +
  theme_minimal(),

ggplot(Turtles4_16_100, aes(x = vote)) +
  geom_histogram(binwidth = 1, fill = "orange", color = "black", alpha = 0.7) +
  labs(title = "Sim 4; 16-100", x = "Vote", y = "Frequency") +
  theme_minimal(),

ggplot(Turtles5_16_100, aes(x = vote)) +
  geom_histogram(binwidth = 1, fill = "purple", color = "black", alpha = 0.7) +
  labs(title = "Sim 5; 16-100", x = "Vote", y = "Frequency") +
  theme_minimal(),

ggplot(Turtles1_18_80, aes(x = vote)) +
  geom_histogram(binwidth = 1, fill = "blue", color = "black", alpha = 0.7) +
  labs(title = "Sim 1; 18-80", x = "Vote", y = "Frequency") +
  theme_minimal(),

ggplot(Turtles2_18_80, aes(x = vote)) +
  geom_histogram(binwidth = 1, fill = "red", color = "black", alpha = 0.7) +
  labs(title = "Sim 2; 18-80", x = "Vote", y = "Frequency") +
  theme_minimal(),

ggplot(Turtles3_18_80, aes(x = vote)) +
  geom_histogram(binwidth = 1, fill = "green4", color = "black", alpha = 0.7) +
  labs(title = "Sim 3; 18-80", x = "Vote", y = "Frequency") +
  theme_minimal(),

ggplot(Turtles4_18_80, aes(x = vote)) +
  geom_histogram(binwidth = 1, fill = "orange", color = "black", alpha = 0.7) +
  labs(title = "Sim 4; 18-80", x = "Vote", y = "Frequency") +
  theme_minimal(),

ggplot(Turtles5_18_80, aes(x = vote)) +
  geom_histogram(binwidth = 1, fill = "purple", color = "black", alpha = 0.7) +
  labs(title = "Sim 5; 18-80", x = "Vote", y = "Frequency") +
  theme_minimal(),

ggplot(Turtles1_18_100, aes(x = vote)) +
  geom_histogram(binwidth = 1, fill = "blue", color = "black", alpha = 0.7) +
  labs(title = "Sim 1; 18-100", x = "Vote", y = "Frequency") +
  theme_minimal(),

ggplot(Turtles2_18_100, aes(x = vote)) +
  geom_histogram(binwidth = 1, fill = "red", color = "black", alpha = 0.7) +
  labs(title = "Sim 2; 18-100", x = "Vote", y = "Frequency") +
  theme_minimal(),

ggplot(Turtles3_18_100, aes(x = vote)) +
  geom_histogram(binwidth = 1, fill = "green4", color = "black", alpha = 0.7) +
  labs(title = "Sim 3; 18-100", x = "Vote", y = "Frequency") +
  theme_minimal(),

ggplot(Turtles4_18_100, aes(x = vote)) +
  geom_histogram(binwidth = 1, fill = "orange", color = "black", alpha = 0.7) +
  labs(title = "Sim 4; 18-100", x = "Vote", y = "Frequency") +
  theme_minimal(),

ggplot(Turtles5_18_100, aes(x = vote)) +
  geom_histogram(binwidth = 1, fill = "purple", color = "black", alpha = 0.7) +
  labs(title = "Sim 5; 18-100", x = "Vote", y = "Frequency") +
  theme_minimal(),

nrow = 4, ncol = 5

)
```
Binding full df and appending sim column to remaining sims
```{r}
Turtles11_16_80$sim <- 11
Turtles12_16_80$sim <- 12
Turtles13_16_80$sim <- 13
Turtles14_16_80$sim <- 14
Turtles15_16_80$sim <- 15
Turtles16_16_80$sim <- 16
Turtles17_16_80$sim <- 17
Turtles18_16_80$sim <- 18
Turtles19_16_80$sim <- 19
Turtles20_16_80$sim <- 20
Turtles11_18_80$sim <- 11
Turtles12_18_80$sim <- 12
Turtles13_18_80$sim <- 13
Turtles14_18_80$sim <- 14
Turtles15_18_80$sim <- 15
Turtles16_18_80$sim <- 16
Turtles17_18_80$sim <- 17
Turtles18_18_80$sim <- 18
Turtles19_18_80$sim <- 19
Turtles20_18_80$sim <- 20
Turtles11_16_100$sim <- 11
Turtles12_16_100$sim <- 12
Turtles13_16_100$sim <- 13
Turtles14_16_100$sim <- 14
Turtles15_16_100$sim <- 15
Turtles16_16_100$sim <- 16
Turtles17_16_100$sim <- 17
Turtles18_16_100$sim <- 18
Turtles19_16_100$sim <- 19
Turtles20_16_100$sim <- 20
Turtles11_18_100$sim <- 11
Turtles12_18_100$sim <- 12
Turtles13_18_100$sim <- 13
Turtles14_18_100$sim <- 14
Turtles15_18_100$sim <- 15
Turtles16_18_100$sim <- 16
Turtles17_18_100$sim <- 17
Turtles18_18_100$sim <- 18
Turtles19_18_100$sim <- 19
Turtles20_18_100$sim <- 20

df_16_80_full <- rbind(Turtles11_16_80, Turtles12_16_80, Turtles13_16_80, Turtles14_16_80, Turtles15_16_80, Turtles16_16_80, Turtles17_16_80, Turtles18_16_80, Turtles19_16_80, Turtles20_16_80, df_16_80_first10)
df_16_100_full <- rbind(Turtles11_16_100, Turtles12_16_100, Turtles13_16_100, Turtles14_16_100, Turtles15_16_100, Turtles16_16_100, Turtles17_16_100, Turtles18_16_100, Turtles19_16_100, Turtles20_16_100, df_16_100_first10)
df_18_80_full <- rbind(Turtles11_18_80, Turtles12_18_80, Turtles13_18_80, Turtles14_18_80, Turtles15_18_80, Turtles16_18_80, Turtles17_18_80, Turtles18_18_80, Turtles19_18_80, Turtles20_18_80, df_18_80_first10)
df_18_100_full <- rbind(Turtles11_18_100, Turtles12_18_100, Turtles13_18_100, Turtles14_18_100, Turtles15_18_100, Turtles16_18_100, Turtles17_18_100, Turtles18_18_100, Turtles19_18_100, Turtles20_18_100, df_18_100_first10)
```



#Data analysis

Modelling spread of vote for default age range 18-100
```{r}
# Descriptive Statistics
summary(df_18_100_full$vote)
mean(df_18_100_full$vote)
median(df_18_100_full$vote)
var(df_18_100_full$vote)
sd(df_18_100_full$vote)

grid.arrange(
# Histogram
ggplot(df_18_100_full, aes(x = vote)) +
  geom_histogram(binwidth = 1, fill = "blue", color = "black", alpha = 0.7) +
  labs(title = "Histogram of Votes", x = "Vote", y = "Frequency") +
  theme_minimal(),

# Box Plot
ggplot(df_18_100_full, aes(y = vote)) +
  geom_boxplot(fill = "red", color = "black", alpha = 0.7) +
  labs(title = "Box Plot of Votes", y = "Vote") +
  theme_minimal(),

# Density Plot
ggplot(df_18_100_full, aes(x = vote)) +
  geom_density(fill = "green4", color = "black", alpha = 0.7) +
  labs(title = "Density Plot of Votes", x = "Vote", y = "Density") +
  theme_minimal(),

# Violin Plot
ggplot(df_18_100_full, aes(x = factor(1), y = vote)) +
  geom_violin(fill = "yellow", color = "black", alpha = 0.7) +
  labs(title = "Violin Plot of Votes", x = "", y = "Vote") +
  theme_minimal() +
  theme(axis.text.x = element_blank(), axis.ticks.x = element_blank()),

nrow = 2, ncol = 2

)
```

Modelling spread of vote for lowered age range 16-100
```{r}
# Descriptive Statistics
summary(df_16_100_full$vote)
mean(df_16_100_full$vote)
median(df_16_100_full$vote)
var(df_16_100_full$vote)
sd(df_16_100_full$vote)

grid.arrange(
# Histogram
ggplot(df_16_100_full, aes(x = vote)) +
  geom_histogram(binwidth = 1, fill = "blue", color = "black", alpha = 0.7) +
  labs(title = "Histogram of Votes", x = "Vote", y = "Frequency") +
  theme_minimal(),

# Box Plot
ggplot(df_16_100_full, aes(y = vote)) +
  geom_boxplot(fill = "red", color = "black", alpha = 0.7) +
  labs(title = "Box Plot of Votes", y = "Vote") +
  theme_minimal(),

# Density Plot
ggplot(df_16_100_full, aes(x = vote)) +
  geom_density(fill = "green4", color = "black", alpha = 0.7) +
  labs(title = "Density Plot of Votes", x = "Vote", y = "Density") +
  theme_minimal(),

# Violin Plot
ggplot(df_16_100_full, aes(x = factor(1), y = vote)) +
  geom_violin(fill = "yellow", color = "black", alpha = 0.7) +
  labs(title = "Violin Plot of Votes", x = "", y = "Vote") +
  theme_minimal() +
  theme(axis.text.x = element_blank(), axis.ticks.x = element_blank()),

nrow = 2, ncol = 2

)
```

Modelling spread of vote for limited age range 18-80
```{r}
# Descriptive Statistics
summary(df_18_80_full$vote)
mean(df_18_80_full$vote)
median(df_18_80_full$vote)
var(df_18_80_full$vote)
sd(df_18_80_full$vote)

grid.arrange(
# Histogram
ggplot(df_18_80_full, aes(x = vote)) +
  geom_histogram(binwidth = 1, fill = "blue", color = "black", alpha = 0.7) +
  labs(title = "Histogram of Votes", x = "Vote", y = "Frequency") +
  theme_minimal(),

# Box Plot
ggplot(df_18_80_full, aes(y = vote)) +
  geom_boxplot(fill = "red", color = "black", alpha = 0.7) +
  labs(title = "Box Plot of Votes", y = "Vote") +
  theme_minimal(),

# Density Plot
ggplot(df_18_80_full, aes(x = vote)) +
  geom_density(fill = "green4", color = "black", alpha = 0.7) +
  labs(title = "Density Plot of Votes", x = "Vote", y = "Density") +
  theme_minimal(),

# Violin Plot
ggplot(df_18_80_full, aes(x = factor(1), y = vote)) +
  geom_violin(fill = "yellow", color = "black", alpha = 0.7) +
  labs(title = "Violin Plot of Votes", x = "", y = "Vote") +
  theme_minimal() +
  theme(axis.text.x = element_blank(), axis.ticks.x = element_blank()),

nrow = 2, ncol = 2

)
```

Modelling spread of vote for lowered and limited age range 16-80
```{r}
# Descriptive Statistics
summary(df_16_80_full$vote)
mean(df_16_80_full$vote)
median(df_16_80_full$vote)
var(df_16_80_full$vote)
sd(df_16_80_full$vote)

grid.arrange(
# Histogram
ggplot(df_16_80_full, aes(x = vote)) +
  geom_histogram(binwidth = 1, fill = "blue", color = "black", alpha = 0.7) +
  labs(title = "Histogram of Votes", x = "Vote", y = "Frequency") +
  theme_minimal(),

# Box Plot
ggplot(df_16_80_full, aes(y = vote)) +
  geom_boxplot(fill = "red", color = "black", alpha = 0.7) +
  labs(title = "Box Plot of Votes", y = "Vote") +
  theme_minimal(),

# Density Plot
ggplot(df_16_80_full, aes(x = vote)) +
  geom_density(fill = "green4", color = "black", alpha = 0.7) +
  labs(title = "Density Plot of Votes", x = "Vote", y = "Density") +
  theme_minimal(),

# Violin Plot
ggplot(df_16_80_full, aes(x = factor(1), y = vote)) +
  geom_violin(fill = "yellow", color = "black", alpha = 0.7) +
  labs(title = "Violin Plot of Votes", x = "", y = "Vote") +
  theme_minimal() +
  theme(axis.text.x = element_blank(), axis.ticks.x = element_blank()),

nrow = 2, ncol = 2

)
```

Joining dataframes for linear model
```{r}
df_18_100_full$age_range <- 1
df_16_100_full$age_range <- 2
df_18_80_full$age_range <- 3
df_16_80_full$age_range <- 4

model1_df <- rbind(df_18_100_full, df_16_100_full)
model2_df <- rbind(df_18_100_full, df_18_80_full)
model3_df <- rbind(df_18_100_full, df_16_80_full)
```



#Modelling impact of age on the vote for hypothesis 1
```{r}

# Round the vote variable to the nearest integer
model1_df$vote <- round(model1_df$vote)

# Convert age.category to a factor
model1_df$age_range <- as.factor(model1_df$age_range)

# Fit a GLM where age.category predicts vote (count outcome)
model1 <- glm(vote ~ age_range, data = model1_df, family = poisson())

# Check the summary of the model
summary(model1)
```
Checking for overdispersion
```{r}
pacman::p_load(AER)
dispersiontest(model1)
# Calculate the ratio of residual deviance to degrees of freedom
ratio1 <- model1$deviance / model1$df.residual
ratio1

```
Ratio is higher than 1, meaning that a negative binomial is more in order
```{r}
# Load the MASS package
library(MASS)

# Fit the Negative Binomial regression model
nb_model1 <- glm.nb(vote ~ age_range, data = model1_df)

# Check the summary of the model
summary(nb_model1)

```



Modelling impact of age on the vote for hypothesis 2
```{r}

# Round the vote variable to the nearest integer
model2_df$vote <- round(model2_df$vote)

# Convert age.category to a factor
model2_df$age_range <- as.factor(model2_df$age_range)

# Fit a GLM where age.category predicts vote (count outcome)
model2 <- glm(vote ~ age_range, data = model2_df, family = poisson())

# Check the summary of the model
summary(model2)
```
Checking for overdispersion
```{r}
dispersiontest(model1)

# Calculate the ratio of residual deviance to degrees of freedom
ratio2 <- model2$deviance / model2$df.residual
ratio2

```

Ratio is higher than 1, meaning that a negative binomial is more in order
```{r}
# Load the MASS package
library(MASS)

# Fit the Negative Binomial regression model
nb_model2 <- glm.nb(vote ~ age_range, data = model2_df)

# Check the summary of the model
summary(nb_model2)

```




Impact of doing both
```{r}

# Round the vote variable to the nearest integer
model3_df$vote <- round(model3_df$vote)

# Convert age.category to a factor
model3_df$age_range <- as.factor(model3_df$age_range)

# Fit a GLM where age.category predicts vote (count outcome)
model3 <- glm(vote ~ age_range, data = model3_df, family = poisson())

# Check the summary of the model
summary(model3)
```

Checking for overdispersion
```{r}
dispersiontest(model1)

# Calculate the ratio of residual deviance to degrees of freedom
ratio3 <- model3$deviance / model3$df.residual
ratio3

```

Ratio is higher than 1, meaning that a negative binomial is more in order
```{r}
# Load the MASS package
library(MASS)

# Fit the Negative Binomial regression model
nb_model3 <- glm.nb(vote ~ age_range, data = model3_df)

# Check the summary of the model
summary(nb_model3)

```


Density plots of age ranges comparatively
```{r}
grid.arrange(
# Model 1
ggplot(model1_df, aes(x = vote, fill = age_range)) +
  geom_density( color = "black", alpha = 0.7) +
  labs(title = "Density Plot of Votes", x = "Vote", y = "Density") +
  theme_minimal(),

# Model 2
ggplot(model2_df, aes(x = vote, fill = age_range)) +
  geom_density( color = "black", alpha = 0.7) +
  labs(title = "Density Plot of Votes", x = "Vote", y = "Density") +
  theme_minimal(),

# Model 3
ggplot(model3_df, aes(x = vote, fill = age_range)) +
  geom_density( color = "black", alpha = 0.7) +
  labs(title = "Density Plot of Votes", x = "Vote", y = "Density") +
  theme_minimal(),

nrow = 2, ncol = 2

)
```


